A comprehensive analysis of natural sequence variation within the <i>Arabidopsis thaliana</i> nuclear auxin signaling pathway

### 2018-01-02 TUTORIAL.Rmd
a few more edits

As it says: "You can access this container using the following IP address and port". This means that if you point your browser to the "ACCESS URL" you will see the version of Rstudio that we've built.

@@

Now when you click on the "kitematic" folder you will see the contents of this folder. Any files you save in this folder will be saved to the folder you mapped on your computer. You can also open files from this folder in RStudio. In the RStudio "Files" pane, navigate to the "manuscript" folder and set it as your working directory (using the "More" button). Click on "manuscript.Rmd" to open the manuscript markdown file.

>>>>

As it says: "You can access this container using the following IP address and port". This means that if you point your browser to the "ACCESS URL" you will see the version of Rstudio that we've built. The username and password are both "rstudio".

@@

Now when you click on the "kitematic" folder you will see the contents of this folder. Any files you save in this folder will be saved to the folder you mapped on your computer. You can also open files from this folder in RStudio. You can save your data and the state of your RStudio session into this folder and it will stay on your computer. If you quit your browser you can navigate back to the same access url, because the docker container will be accessible unless you stop it in kitematic.

In the RStudio "Files" pane, navigate to the "manuscript" folder and set it as your working directory (using the "More" button). Click on "manuscript.Rmd" to open the manuscript markdown file.

### 2018-01-02 manuscript/manuscript.Rmd
a few more edits

# Results  
## TIR1/AFB genes  
[@gray_identification_1999; @kepinski_auxininduced_2004; @tan_mechanism_2007; @dezfulian_oligomerization_2016; @wu_evolution_2017b]

@@

### Group A Aux/IAAs

### Group B Aux/IAAs

### Group C Aux/IAAs

## TPL/TPR genes

@@

### Class A ARFs

### Class B ARFs

### Class C ARFs

>>>>

# Results  
## TIR1/AFB genes  
Romi
[@gray_identification_1999; @kepinski_auxininduced_2004; @tan_mechanism_2007; @dezfulian_oligomerization_2016; @wu_evolution_2017b]

@@

### Group A Aux/IAAs
Britney

### Group B Aux/IAAs
Mollye/Alex

### Group C Aux/IAAs
Mega/Alex

## TPL/TPR genes  
Alex

@@

### Class A ARFs
Amy

### Class B ARFs
Andrew/Arjun

### Class C ARFs
Hardik
